Crowdy: Social Crowd Visualization

### 2011-04-28 docs/crowdy_gui.tex
added Prateek's questions to likert scale, added info about the network graph

The list view as shown in Figure \ref{fig:ListView} requires a dynamic table in which it displays as many rows as the amount of crowds returned by the API. Concretely, we issue a jQuery for all the available crowds in the database. The javascript helps to create the dynamic table which includes the following columns: Period, Users and size of the crowd.Once a row of crowd is clicked, a slide down box with detail information(crowd user network, tweets) will be shown below. There are three types of information available for users to choose from: Network, Tweets and Graph and a ``star'' mark.

Each crowd has a star-feature attached to it which can be used by the user to mark his favourite crowds.This feature is present in the detailed view of the crowd which is activated as said earlier by selecting the row of a crowd.This is used to rearrange the list of crowds with the starred crowds appearing at the top whenever the user comes back to the list view.The user can mark any crowd as starred or unstar the ones that are already starred at any point of time.

@@

The default view is the Network information as shown in figure \ref{fig:NetworkInList} where nodes represent users, and edges represent the tweets. The network graph show the relationship of the users involved in this particular crowd based on the tweets mentioning activities. A thicker edge between two users indicate a tighter mentioning action between them. We plan to add the ability to drill down even more.  When the analyst clicks on a node, we can give the analyst more information about the user that was clicked on. When the analyst clicks on an edge, we can show the conversation between two users.
 %Jeff, would you like to talk more about the network%

@@

The pilot study we propose contains basic demographic information, five questions with a
five point Likert scale (i.e., strongly agree, agree
neutral, disagree, and strongly disagree), and four open questions. The
Likert scale questions are listed below:

\begin{itemize}
\item The interface for timeline view is easy to use.
\item The interface for list view is easy to use.
\item The search feature for timeline view is easy to use.
\item The search feature for list view is easy to use.
\item I could use the search features to find crowds that I was interested in.
\end{itemize}

@@

>>>>

The list view as shown in Figure \ref{fig:ListView} requires a dynamic table in
which it displays as many rows as the amount of crowds returned by the API.
Concretely, we issue an HTTP request to get the crowds in the database in a
JSON object. The javascript creates the dynamic table which includes the
following columns: Period, Users and size of the crowd. Once a row of crowd is
clicked, a slide down box with detail information(crowd user network, tweets)
will be shown below. There are three types of information available for users
to choose from: Network, Tweets and Graph and a ``star'' mark.

Each crowd has a star-feature attached to it which can be used by the user to
mark his favourite crowds. This feature is present in the detailed view of the
crowd which is activated as said earlier by selecting the row of a crowd. This
is used to rearrange the list of crowds with the starred crowds appearing at
the top whenever the user comes back to the list view. The user can mark any
crowd as starred or unstar the ones that are already starred at any point of
time.

@@

The default view is the Network information as shown in figure
\ref{fig:NetworkInList} where nodes represent users, and edges represent the
tweets. The network graph show the relationship of the users involved in this
particular crowd based on the tweets mentioning activities. A thicker edge
between two users indicates more tweets sent between that pair of users. In the
future work section of this paper, we discuss ways that this could be improved
to let the user drill down even more.

@@

The pilot study we propose consists of two parts. First, we will ask the users
to use our system to find seveal conversations that they find interesting.
Next, we will use a questionnaire to gather basic demographic information and
answers to seven questions with a five point Likert scale (i.e., strongly
agree, agree neutral, disagree, and strongly disagree) and four open questions.
The Likert scale questions are listed below:

\begin{itemize}
\item The interface for timeline view is easy to use.
\item The interface for list view is easy to use.
\item The search feature for timeline view is easy to use.
\item The search feature for list view is easy to use.
\item I could use the search features to find crowds that I was interested in.
\item The star feature helped me organize crowds.
\item When I star a crowd, all the crowds on the page should be re-arranged in real time to place the starred crowd on top.
\end{itemize}

@@

Fourth, we can make the network view more interactive. For example, when the
analyst clicks on a node, we can give the analyst more information about the
Twitter user that was clicked on. When the analyst clicks on an edge, we can show the
conversation between those two users.
